---
title: "Sandia Wetlands "
author: "Paul Mark", "Allison Chan"
date: "7/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown SQL for generating Sandia Wetlands analytical data

SELECT v_lanl_report_chem.*,  <br/>
  v_lanl_report_chem.location_id_alias AS location_id_alias1 <br/>
FROM v_lanl_report_chem <br/>
WHERE (v_lanl_report_chem.location_id_alias LIKE 'SWA%') OR <br/>
  (v_lanl_report_chem.location_id_alias LIKE 'SCPZ%') OR <br/>
  (v_lanl_report_chem.location_id_alias = 'E121') OR <br/>
  (v_lanl_report_chem.location_id_alias = 'E122') OR <br/>
  (v_lanl_report_chem.location_id_alias = 'E123') OR <br/>
  (v_lanl_report_chem.location_id_alias = 'NPDES Outfall 001') <br/>
  
This file is saved in the shared Github repository PaulJMark/SandiaWetlandsPerformance.
  
Go to the shared directory. Click on the file. Download to a local directory.
  
Unzip the file into your local directory.  Run the following code and observe 103,954 analytical records are present


```{r}
library(readr)
san <- read_csv("EIM_EXPORT_07_04_2018.csv", 
                col_types = list('Sample Date' = col_date("%m/%d/%Y"),
                                 'Display Sample Date'= col_date("%m/%d/%Y"),
                                 'Sampling Event End Date'= col_date("%m/%d/%Y"),
                                 'Display End Sample Date'= col_date("%m/%d/%Y"),
                                 'Lab Receipt Date'= col_date("%m/%d/%Y"),
                                 'Display Lab Receipt Date'= col_date("%m/%d/%Y"),
                                 'Analysis Date'= col_date("%m/%d/%Y"),
                                 'Display Analysis Date'= col_date("%m/%d/%Y"),
                                 '% Moisture' = col_double(),
                                 'Uploaded Date'= col_date("%m/%d/%Y"),
                                 'Display Upload Date'= col_date("%m/%d/%Y"),
                                 'Last Modified Date'= col_date("%m/%d/%Y"),
                                 'Display Last Modified Date'= col_date("%m/%d/%Y"),
                                 'Validated Date'= col_date("%m/%d/%Y"),
                                 'Display Validation Date'= col_date("%m/%d/%Y"),
                                 'Web Publish Date'= col_date("%m/%d/%Y")))
names(san)<-make.names(names(san),unique = TRUE)

summary(san)

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
